---
title: "HSF Exercise"
author: "Brian J. Smith"
date: "26 January 2022"
output: 
  html_document:
    theme: default
    css: "../css/exercises.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

Let's apply what we've learned about HSFs. Refer to the lecture slides (<a href="05a_lecture.html" target="_blank" rel="noopener noreferrer">05a_lecture.html</a>) and the walkthrough code (`05b_walkthrough.R`) as a refresher.

We encourage you to use your own data for this exercise. We will be available while you are working to answer any questions.

If you don't have your own data, you can use example data built into `amt`. You can access the fisher data and some covariate rasters like this:

```{r amt_fisher, eval = FALSE}
# Load `amt`
library(amt)

# Location data as 'track_xyt'
dat <- amt_fisher

# Habitat data as list
hab <- amt_fisher_covar

```

We will go over how to model multiple animals in a later module, so for now,
subset your data (or the fisher data) to just one animal.

## Instructions

1. Load your data or the `amt` fisher data. Subset to a single individual.

    * Recall that HSFs assume each point is independent and that all habitat is available.
    * If you have high temporal resolution location data, you might want to subset to a coarser temporal resolution to maintain independence.

2. Before you get started, consider your habitat variables. 

    * Decide *a priori* whether each variable represents a resource, risk, or condition. 
    * Make sure you distinguish between continuous and categorical (like landcover) variables.
    * Include your thoughts about each variable as comments in your analysis script.
    
3. Fit a third-order HSF. *I.e.*, sample available points from within the home range of your individual.

    * Make sure the form of each variable matches your *a priori* hypotheses about it from above (*i.e.*, are your continuous conditions modeled as parabolas?).
    * Use the logistic regression approach by sampling a large number of available locations. Make sure to give the used locations a weight of 1 and the available locations large weights.
    
4. Plot the RSS (or log-RSS) for the range of each of your habitat variables.

    * What does each plot tell you about the biology of your system?
    * Be sure to include confidence intervals.

