---
title: "iSSF Pt 2 Exercise"
author: "Brian J. Smith"
date: "27 January 2022"
output: 
  html_document:
    theme: default
    css: "../css/exercises.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

Let's apply what we've learned about HSFs. Refer to the lecture slides (<a href="08a_lecture.html" target="_blank" rel="noopener noreferrer">08a_lecture.html</a>) and the walkthrough code (`08b_walkthrough.R`) as a refresher.

We encourage you to use your own data for this exercise. We will be available while you are working to answer any questions.

If you don't have your own data, you can use some sample coyote data from UT. These data were published by Mahoney et al. (2017) [here](https://www.datarepository.movebank.org/handle/10255/move.590). These data were originally used in this manuscript:

> Mahoney PJ, Young JK (2016) Uncovering behavioural states from animal activity and site fidelity patterns. Methods in Ecology and Evolution 8(2): 174–183. [doi:10.1111/2041-210X.12658](https://doi.org/10.1111/2041-210X.12658)

We've already downloaded and processed the data, which you can find in `data/coyote_cougar.csv`. We've also downloaded and processed some environmental raster data for you to use, which you can find as a multi-band GeoTiff in `data/coyote_cougar_habitat.tif`.

Habitat layers are:  

- Elevation (m)
- Tree cover (%)
- Herbaceous biomass (kg/ha)
- Distance to nearest road (m)

We will go over how to model multiple animals in a later module, so for now,
subset your data to just one animal.

```{r data, eval = FALSE}
# Load `tidyverse` and `raster`
library(tidyverse)
library(raster)

# Location data as 'track_xyt'
dat <- read_csv("data/coyote_cougar.csv") %>% 
  # Subset to just the coyote
  filter(id == "C028")

# Habitat data as stack
hab <- stack("data/coyote_cougar_habitat.tif")
names(hab) <- c("elevation", "trees", "biomass", "dist_to_road")

```

## Instructions

1. Load your data or the example data. Subset to a single individual.

    * Recall that iSSFs assume a constant step duration. Make sure your data are (approximately) regularly sampled before you continue.
    * You will want a fairly large sample size as your model grows in parameters by including interaction terms.
    
2. Before you get started, consider your habitat variables. 

    * Decide *a priori* whether each variable represents a resource, risk, or condition. 
    * Should any of your habitat covariates interact with each other? Why?
    * Which of your covariates might affect the movement process? 
    * Include your thoughts about each variable as comments in your analysis script.
    
3. Fit an iSSF, with at least one interaction.

    * Make sure the form of each variable matches your *a priori* hypotheses about it from above. Pay careful attention to understand what your interaction terms mean.
    
4. Make at least one plot showing the RSS (or log-RSS) for one of your habitat variables.

    * What does this plot tell you about the biology of your system?
    
5. Make at least one plot showing the step-length or turn-angle distribution for your animal.

    * If you have interactions with step-length or turn-angle, make sure you show this.
    

<br>
<hr>
<br>


