---
title: "Home Ranges Exercise"
author: "Brian J. Smith"
date: "24 January 2022"
output: 
  html_document:
    theme: default
    css: "../css/exercises.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

Let's apply what we've learned about home ranges. Refer to the lecture slides (<a href="02a_lecture.html" target="_blank" rel="noopener noreferrer">02a_lecture.html</a>) and the walkthrough code (`02b_walkthrough.R`) as a refresher.

We encourage you to use your own data for this exercise. We will be available while you are working to answer any questions.

If you don't have your own data, you can use example data built into `amt`. You can access the fisher data like this:

```{r amt_fisher, eval = FALSE}
# Load `amt`
library(amt)

# Location data as 'track_xyt'
dat <- amt_fisher

```

You likely have more than one individual in your own data, and `amt_fisher` also has 4 individuals. 

## Instructions

1. Load in your data or the `amt_fisher` dataset. If you're working with your own data, format it as a `track_xyt` object using `amt::make_track()`.
  
2. Create a nested `data.frame` by nesting by individual ID (or burst, if you have separate bursts in your data).
  
3. Fit a home range of your choice for each individual (feel free to fit more than one home range type). Fit at least two isopleths per home range, *e.g.*, 95% and 50%. 
    
4. Compute the area of each home range polygon. Convert the area to reasonable units for your study animal, such as ha or km^2^.
  
5. Make a map with each individual's home range. It's up to you whether you want all your individuals on a single map or one map per individual.